Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-26 manuscript/manuscript.tex
Improve enumerated figure captions

\begin{figure*}
\centering
\includegraphics[width=\linewidth]
    {figures/density-based-discretization-algorithm.pdf}
\caption{
    Example application of the density-based discretization algorithm to a non-linear
    density function.
    (a) The normalised density function $\rho_n(r')$ (blue), current boundaries of the
    tesseroid (orange dots), and the linear density function $\rho_l(r')$ (orange line).
    The dashed red line represents the maximum density difference $\Delta \rho (r')$ at
    which the tesseroid would be divided (assuming that the
    inequality~\ref{eq:delta-density} is not satisfied).
    (b) Second iteration of the algorithm with a new linear density function and maximum
    density difference. The tesseroid would be divided at the depth indicated by the
    dashed red line.
    (c) Third iteration of the algorithm.
    (d) Final output of the density-based discretization, assuming that all four new
    tesseroids satisfy inequality~\ref{eq:delta-density}.
}
\label{fig:density-discretization-algorithm}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/neuquen-basin.pdf}
\caption{
    Gravitational effects of the Nequ\'en sedimentary basin modelled
    using tesseroids with an exponential density function of depth.
    (a) Topography of the Neuqu\'en Basin (in km) and its location in South America,
    (b) thickness of the sedimentary basin \citep[in meters;][]{Heine2007},
    (c) resulting gravitational potential $V$,
    (d) resulting vertical component of the gradient ($g_z$),
    calculated at 10km of height over the mean Earth radius.
}
\label{fig:neuquen-basin}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/neuquen-basin-diffs.pdf}
\caption{
    Differences between the gravitational fields generated by the tesseroid model of the
    Neuquen basin with an exponential density contrast and with a homogenenous and
    linear density variation.
    (a)-(b) Differences on $V$ and $g_z$ between the exponential density model and the
    homogenenous density one,
    (c)-(f) differences on $V$ and $g_z$ between the exponential density model and the
    linear density one,
    calculated at 10km of height over the mean Earth radius.
}
\label{fig:neuquen-basin-diffs}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=\linewidth]
    {figures/density-based-discretization-algorithm.pdf}
\caption{
    Example application of the density-based discretization algorithm to a non-linear
    density function.
    (a)~The normalised density function $\rho_n(r')$ (blue), current boundaries of the
    tesseroid (orange dots), and the linear density function $\rho_l(r')$ (orange line).
    The dashed red line represents the maximum density difference $\Delta \rho (r')$ at
    which the tesseroid would be divided (assuming that the
    inequality~\ref{eq:delta-density} is not satisfied).
    (b)~Second iteration of the algorithm with a new linear density function and maximum
    density difference. The tesseroid would be divided at the depth indicated by the
    dashed red line.
    (c)~Third iteration of the algorithm.
    (d)~Final output of the density-based discretization, assuming that all four new
    tesseroids satisfy inequality~\ref{eq:delta-density}.
}
\label{fig:density-discretization-algorithm}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/neuquen-basin.pdf}
\caption{
    Gravitational effects of the Nequ\'en sedimentary basin modelled
    using tesseroids with an exponential density function of depth.
    (a)~Topography of the Neuqu\'en Basin (in km) and its location in South America,
    (b)~thickness of the sedimentary basin \citep[in meters;][]{Heine2007},
    (c)~resulting gravitational potential $V$,
    (d)~resulting vertical component of the gradient ($g_z$),
    calculated at 10km of height over the mean Earth radius.
}
\label{fig:neuquen-basin}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/neuquen-basin-diffs.pdf}
\caption{
    Differences between the gravitational fields generated by the tesseroid model of the
    Neuquen basin with an exponential density contrast and with a homogenenous and
    linear density variation.
    \mbox{(a)-(b)}~Differences on $V$ and $g_z$ between the exponential density model
    and the homogenenous density one,
    \mbox{(c)-(f)}~differences on $V$ and $g_z$ between the exponential density model
    and the linear density one, calculated at 10km of height over the mean Earth radius.
}
\label{fig:neuquen-basin-diffs}
\end{figure*}
